### 2022-03-22 paper/output/document/thesis_2_methods.tex
i hate don knuth

Other choices of components, such as another ethical theory, a different logic, or a different theorem 
prover could be made. Flaws with these components are limitations of my system, but do not 
indict logic-programming-based automated ethics more generally. My thesis seeks to 
both present a specific implementation of automated ethics and to argue for a particular approach 
to automating ethical reasoning more generally and these choices are relevant to the former goal but 
not to the latter.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsection{Choice to Automate Kantian Ethics \label{whykant}%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
In this thesis, I automate Kantian ethics. In 2006, Powers posited that deontological theories are 
attractive candidates for automation because rules are generally computationally tractable \cite[1]{powers}. 
Intuitively, algorithms are procedures for problem solving and Kantian ethics (which is a kind 
of deontological theory) offers one such 
procedure for the problem of making ethical judgements. I will make this intuition precise by
arguing that Kantian ethics is natural to formalize because it prescribes moral rules that require 
little additional data about the world and are easy to represent to a computer. I argue that, compared to 
consequentialism and virtue ethics,\footnote{Technically, virtue ethics and
consequentialism are broad ethical traditions, while Kantian ethics is a specific ethical theory within
deontology, the third major ethical tradition. However, Kantian ethics is not merely a kind of deontology
but is widely regarded as deontology's central representative \citep{sepdeont}. Deontology's comparatively 
greater focus on Kant means that my choice of Kant as a guiding figure is less controversial for deontologists 
than, for example, the choice of Bentham as the guiding figure of consequentialism. Given that most deontological
theories have some connection to or basis in Kantian ethics, I choose to focus on Kantian ethics, instead
of deontology more broadly. } Kantian ethics is more amenable to automation.

@@

To solve this problem, some consequentialists reject aggregation entirely and instead prefer wholistic
evaluations of a state of affairs. While this approach no longer requires that an 
aggregation algorithm, an automated ethical system still needs to calculate a goodness measurement for a state of 
affairs. Whereas before the system could restrict its analysis to a single person, the algorithm must now 
evaluate an entire state wholistically. As consequentialists modulate between aggregation 
and wholistic evaluation, they face a tradeoff between the difficulty of aggregation and the complexity 
of goodness measurements for large states of affairs.%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkuptext}%
\noindent \textbf{Prior Attempts to Formalize Consequentialism}%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkuptext}%
Because of its intuitive appeal, computer scientists have tried to formalize consequentialism in the past.
These efforts cannot escape the challenges outlined above. For example, Abel et al. represent ethics as a
Markov Decision Process (MDP), with reward functions customized to particular ethical dilemmas 
\citep[3]{util1}. While this is a convenient representation, it either leaves unanswered or 
takes implicit stances on the debates above. It assumes that consequences can be aggregated just as 
reward is accumulated in an MDP, according to a weighted sum, with future consequences weighted less
than immediate ones. It leaves open the question of what the reward function is and thus doesn't 
specify a theory of the good, arguably the defining trait of consequentialism. Anderson and Anderson
face similar issues with their hedonistic\footnote{Recall that hedonism views pleasure as good
and pain as bad.} act-utilitarian automated reasoner, which chooses hedonism as the theory of the good \citep[2]{util2}. 
Their proposal assumes that pleasure and pain can be 
given numeric values and that these values can be aggregated with a simple sum, taking an implicit
stance on the aggregation question. Other attempts to automate consequentialist ethics will suffer 
similar problems because, at some point, a usable automated consequentialist moral agent must
resolve the above debates.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsubsection{Virtue Ethics\label{virtueethics}%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
Virtue ethics places the virtues, or traits that constitute a good moral character and make 
their possessor good, at the center \citep{vesep}. For example, Aristotle describes virtues as the 
traits that enable human flourishing. Just as consequentialists define ``good'' consequences, virtue 
ethicists present a list of virtues, such as the Buddhist virtue of equanimity \citep{mcrae}. An automated virtue 
ethical agent will need to commit to a list of virtues, a controversial choice. 
Virtue ethicists robustly debate which traits qualify as virtues, what each virtue actually means, and 
what kinds of feelings or attitudes must accompany virtuous action.

@@

Machine learning approaches like the Delphi system \citep{delphi} mentioned in Chapter \ref{intro} also may suffer explanability 
problems that my logic-programming, theorem-prover
approach does not face. Many machine learning algorithms cannot sufficiently explain their 
decisions to a human being and often find patterns in datasets that don't 
cohere with the causes that a human being would identify \citep{puiutta}. While there is significant activity 
and progress in explainable machine learning, interactive theorem provers are designed to be explainable 
at the outset. Isabelle can show the axioms and lemmas it used in constructing a proof, 
allowing a human being to reconstruct the proof independently if they wish. This is not an 
intractable problem for machine learning approaches to computational ethics, but is one reason to 
prefer logical approaches.\footnote{This argument about explanability is in the context of virtue ethics and 
machine learning. It also applies to a broader class of work in automated ethics 
that uses a ``bottom-up'' approach, in which a system learns moral judgements from prior judgements. 
I will extend this argument to general bottom-up approaches in Section \ref{relatedwork}.}%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsubsection{Kantian Ethics \label{kantianethics}%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
Kant's theory is centered 
on practical reason, which is the kind of reason that we 
use to decide what to do. In \emph{The Groundwork of the Metaphysics of Morals}, Kant explains that 
rational beings are unique because we act ``in accordance with 
the representations of laws'' \citep[26]{groundwork}. A ball thrown into the air acts 
according to the laws of physics. It cannot ask itself, ``Should I fall back to the ground?'' 
It simply falls. A rational being, on the other hand, can ask, ``Should I act on this reason?"''
As Korsgaard describes it, when choosing which desire to act on, ``it is as if there is something over 
and above all of your desires, something which is you, and which chooses which desire to act on'' \citep[100]{sources}. 
Rational beings are set apart by this reflective capacity. We are purposive and 
our actions are guided by practical reason. We have reasons for acting, even when these reasons are
opaque to us. This reflective choosing, or operation of practical reason, is what Kant calls the \emph{will}.

@@

Common sense is also relevant when applying the universalizability test itself. Consider the example
maxim ``When broke, I will falsely promise to repay a loan
to get some quick cash.'' This maxim fails the universalizability test because in a world where everyone
falsely promises to repay loans, no one will believe promises anymore, so the maxim will no longer serve
its intended purpose (getting some quick cash). Making this judgement requires understanding enough about
the system of promising to realize that it breaks down if everyone abuses it in this manner. This is a
kind of common sense reasoning that an automated Kantian agent would need. This need is not unique to
Kantian ethics; consequentialists agents need common sense to determine the consequences of 
an action and virtue ethical agents need common sense to determine which virtues an action
reflects. For example, in the case of virtue ethics, in order to see that saving a baby from a lion 
requires courage, a reasoner must have enough background knowledge to know that lions are scary. Making any 
ethical judgement requires robust conceptions of the action at hand, but Kantian ethics requires far less common sense 
than a consequentialism or virtue ethics.\footnote{
In Sections \ref{joking} and \ref{murderer}, I use my system to demonstrate that Kantian ethics requires relatively lightweight, uncontroversial definitions 
of concepts like falsely promising.} All
moral theories evaluating falsely promising will a robust definition of promising, 
but consequentialism and virtue ethics will require more information than Kantian ethics.
Thus, although the need for common sense poses a challenge to automated
Kantian ethics, this challenge is more acute for consequentialism or virtue ethics.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsubsection{The Formula of Universal Law \label{whyful}%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
Kant presents three formulations, or versions, 
of what he calls the ``supreme law of morality,'' but I focus on the first of these three. In this section, 
I argue that the Formula of Universal Law, specifically, is the easiest part of Kantian ethics to automate
and the most generalizable.

@@

Those who do not believe that all three formulations of the categorical imperative are equivalent
understand the FUL as the strongest or most foundational, and thus an appropriate initial choice for 
automation. Korsgaard characterizes the three formulations of the categorical
imperative according to Rawls' general and special conception of justice \cite{theoryofjustice}. The general conception applies
universally and can never be violated, while the special conception represents an ideal for us to
live towards that may not be possible to achieve. For example, the special conception may require that we prefer some job applicants
over others in order to remedy historical injustice, and the general conception may require that such
inequalities always operate in the service of the least privileged \citep[19]{KorsgaardRTL}. Korsgaard
argues that the Formula of Universal Law represents Kant's general conception of justice, and the Formula of 
Humanity represents his special conception. The FUL's prescriptions can never be violated, even in the most
non-ideal circumstances imaginable, but the FUH is merely an ideal to strive towards. Thus, the FUL 
generates stronger requirements than the other two formulations and reflects 
the bare minimum standard of Kant's ethics. Because the FUL's prescriptions outweigh those of the other two formulations,
it serves as a functional, minimal version of Kantian ethics.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsection{Dyadic Deontic Logic \label{ddl}%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
I formalize Kantian ethics by representing the Formula of Universal Law as an axiom on top of a base
logic. In this section, I present the logical background necessary to understand my work and my 
choice of Dyadic Deontic Logic (DDL).

@@

\isamarkupcmt{The blue texte below is an example of typical Nitpick output. In this case, Nitpick successfully found a model 

@@

which is why this theorem was so easy to prove.%

@@

%:%94=50%:%
%:%103=53%:%

@@

%:%123=63%:%
%:%127=65%:%

@@

%:%155=91%:%
%:%159=94%:%

@@

%:%179=112%:%
%:%183=114%:%

@@

%:%203=132%:%
%:%207=135%:%

@@

%:%225=152%:%
%:%234=155%:%

@@

%:%262=173%:%
%:%266=175%:%

@@

%:%294=201%:%
%:%295=202%:%
%:%304=205%:%

@@

%:%370=261%:%
%:%371=262%:%
%:%372=263%:%
%:%376=266%:%

@@

%:%397=285%:%
%:%398=286%:%
%:%399=287%:%
%:%403=290%:%

@@

%:%431=316%:%
%:%432=317%:%
%:%433=318%:%
%:%434=319%:%
%:%443=321%:%

@@

%:%501=369%:%
%:%502=370%:%
%:%511=372%:%

@@

%:%583=435%:%
%:%584=436%:%
%:%593=439%:%

@@

%:%609=445%:%
%:%610=446%:%
%:%619=449%:%

@@

%:%632=452%:%

@@

%:%635=455%:%
%:%636=455%:%
%:%637=455%:%
%:%638=455%:%
%:%640=456%:%
%:%641=456%:%
%:%642=457%:%
%:%643=457%:%
%:%644=457%:%
%:%645=457%:%
%:%647=458%:%
%:%648=459%:%

@@

%:%652=472%:%

@@

%:%655=475%:%
%:%656=475%:%
%:%657=475%:%
%:%658=475%:%
%:%659=476%:%
%:%660=476%:%

@@

%:%665=480%:%

@@

%:%668=483%:%
%:%669=483%:%
%:%670=507%:%
%:%671=508%:%

@@

%:%675=511%:%
%:%676=512%:%
%:%684=517%:%

@@

%:%701=524%:%
%:%702=525%:%
%:%706=539%:%
%:%708=540%:%
%:%709=540%:%
%:%710=541%:%
%:%712=542%:%
%:%713=543%:%
%:%714=543%:%
%:%715=544%:%
%:%716=544%:%
%:%717=545%:%
%:%719=546%:%
%:%722=547%:%
%:%724=548%:%
%:%725=548%:%
%:%726=549%:%
%:%728=550%:%
%:%731=567%:%
%:%732=568%:%
%:%734=569%:%

@@

%:%736=570%:%
%:%737=571%:%

@@

%:%739=572%:%
%:%740=573%:%
%:%741=573%:%
%:%742=574%:%
%:%744=575%:%
%:%745=576%:%
%:%748=577%:%
%:%750=578%:%
%:%751=578%:%
%:%752=579%:%
%:%754=580%:%

@@

%:%760=588%:%
%:%761=589%:%
%:%763=592%:%
%:%764=592%:%
%:%765=592%:%
%:%767=592%:%
%:%771=592%:%
%:%772=592%:%
%:%774=593%:%
%:%775=594%:%
%:%776=594%:%

@@

%:%779=596%:%
%:%780=597%:%

@@

%:%792=601%:%

>>>>

Other choices of components, such as another ethical theory, a different logic, or a different theorem 
prover could be made. Flaws with these components are limitations of my system, but do not 
indict logic-based automated ethics more generally. My thesis seeks to 
both present a specific implementation of automated ethics and to argue for a particular approach 
to automating ethical reasoning more generally and these choices are relevant to the former goal but 
not to the latter.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsection{Choice to Automate Kantian Ethics \label{whykant}%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
In this thesis, I automate Kantian ethics. In 2006, Powers posited that deontological theories are 
attractive candidates for automation because rules are generally computationally tractable \cite[1]{powers}. 
Intuitively, algorithms are procedures for problem solving and Kantian ethics (which is a kind 
of deontological theory) offers one such 
procedure for the problem of making ethical judgements. I will make this intuition precise by
arguing that Kantian ethics is more natural to formalize than consequentialism or virtue ethics\footnote{Technically, virtue ethics and
consequentialism are broad ethical traditions, while Kantian ethics is a specific ethical theory within
deontology, the third major ethical tradition. However, Kantian ethics is not merely a kind of deontology
but is widely regarded as deontology's central representative \citep{sepdeont}. Deontology's comparatively 
greater focus on Kant means that my choice of Kant as a guiding figure is less controversial for deontologists 
than, for example, the choice of Bentham as the guiding figure of consequentialism. Given that most deontological
theories have some connection to or basis in Kantian ethics, I choose to focus on Kantian ethics, instead
of deontology more broadly. } because it prescribes moral rules that require 
little additional data about the world and are easy to represent to a computer.

@@

To solve this problem, some consequentialists reject aggregation entirely and instead prefer holistic
evaluations of a state of affairs. While this approach no longer requires that an 
aggregation algorithm, an automated ethical system still needs to calculate a goodness measurement for a state of 
affairs. Whereas before the system could restrict its analysis to a single person, the algorithm must now 
evaluate an entire state holistically. As consequentialists modulate between aggregation 
and holistic evaluation, they face a tradeoff between the difficulty of aggregation and the complexity 
of goodness measurements for large states of affairs.%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkuptext}%
\noindent \textbf{Prior Attempts to Formalize Consequentialism}%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkuptext}%
Because of its intuitive appeal, computer scientists have tried to formalize consequentialism in the past.
These efforts cannot escape the challenges outlined above. For example, Abel et al. represent ethics as a
Markov Decision Process (MDP), with reward functions customized to particular ethical dilemmas 
\citep[3]{util1}. While this is a convenient representation, it either leaves unanswered or 
takes implicit stances on the debates above. It assumes that consequences can be aggregated just as 
reward is accumulated in an MDP, according to a weighted sum, with future consequences weighted less
than immediate ones. It leaves open the question of what the reward function is and thus doesn't 
specify a theory of the good, arguably the defining trait of consequentialism. Anderson and Anderson
face similar issues with their hedonistic\footnote{Recall that hedonism views pleasure as good
and pain as bad.} act-utilitarian automated reasoner, which chooses hedonism as the theory of the good \citep[2]{util2}. 
Their proposal assumes that pleasure and pain can be 
given numeric values and that these values can be aggregated with a simple sum, taking an implicit
stance on the aggregation question. Other attempts to automate consequentialist ethics will suffer 
similar problems because, at some point, a usable automated consequentialist moral agent must
resolve the above debates.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsubsection{Virtue Ethics\label{virtueethics}%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
Virtue ethics places the virtues, or traits that constitute a good moral character and make 
their possessor good, at the center \citep{vesep}. For example, Aristotle describes virtues as the 
traits that enable human flourishing. Just as consequentialists define ``good'' consequences, virtue 
ethicists present a list of virtues, such as the Buddhist virtue of equanimity \citep{mcrae}. An automated virtue 
ethical agent will need to commit to a list of virtues, a controversial choice. 
Virtue ethicists robustly debate which traits qualify as virtues, what each virtue actually means, and 
what kinds of feelings or attitudes must accompany virtuous action.

@@

Machine learning approaches like the Delphi system \citep{delphi} mentioned in Chapter \ref{intro} also may suffer explanability 
problems that my system does not face. Many machine learning algorithms cannot sufficiently explain their 
decisions to a human being and often find patterns in datasets that don't 
cohere with the causes that a human being would identify \citep{puiutta}. While there is significant activity 
and progress in explainable machine learning, interactive theorem provers are designed to be explainable 
at the outset. Isabelle can show the axioms and lemmas it used in constructing a proof, 
allowing a human being to reconstruct the proof independently if they wish. This is not an 
intractable problem for machine learning approaches to computational ethics, but is one reason to 
prefer logical approaches.\footnote{This argument about explanability is in the context of virtue ethics and 
machine learning. It also applies to a broader class of work in automated ethics 
that uses a ``bottom-up'' approach, in which a system learns moral judgements from prior judgements. 
I will extend this argument to general bottom-up approaches in Section \ref{relatedwork}.}%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsubsection{Kantian Ethics \label{kantianethics}%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
Kant's theory is centered on practical reason, which is the kind of reason that we 
use to decide what to do. In \emph{The Groundwork of the Metaphysics of Morals}, Kant explains that 
rational beings are unique because we act ``in accordance with 
the representations of laws'' \citep[26]{groundwork}. A ball thrown into the air acts 
according to the laws of physics. It cannot ask itself, ``Should I fall back to the ground?'' 
It simply falls. A rational being, on the other hand, can ask, ``Should I act on this reason?"''
As Korsgaard describes it, when choosing which desire to act on, ``it is as if there is something over 
and above all of your desires, something which is you, and which chooses which desire to act on'' \citep[100]{sources}. 
Rational beings are set apart by this reflective capacity. We are purposive and 
our actions are guided by practical reason. We have reasons for acting, even when these reasons are
opaque to us. This reflective choosing, or operation of practical reason, is what Kant calls the \emph{will}.

@@

Common sense is also relevant when applying the universalizability test itself. Consider the example
maxim ``When broke, I will falsely promise to repay a loan
to get some quick cash.'' This maxim fails the universalizability test because in a world where everyone
falsely promises to repay loans, no one will believe promises anymore, so the maxim will no longer serve
its intended purpose (getting some quick cash). Making this judgement requires understanding enough about
the system of promising to realize that it breaks down if everyone abuses it in this manner. This is a
kind of common sense reasoning that an automated Kantian agent would need. This need is not unique to
Kantian ethics; consequentialists agents need common sense to determine the consequences of 
an action and virtue ethical agents need common sense to determine which virtues an action
reflects. For example, in the case of virtue ethics, in order to see that saving a baby from a lion 
requires courage, a reasoner must have enough background knowledge to know that lions are scary. Making any 
ethical judgement requires robust conceptions of the action at hand, but Kantian ethics requires far less common sense 
than consequentialism or virtue ethics.\footnote{
In Sections \ref{joking} and \ref{murderer}, I use my system to demonstrate that Kantian ethics requires relatively lightweight, uncontroversial definitions 
of concepts like falsely promising.} All moral theories evaluating falsely promising need a robust 
definition of promising, but consequentialism and virtue ethics will require more information than Kantian ethics.
Thus, although the need for common sense poses a challenge to automated
Kantian ethics, this challenge is more acute for consequentialism or virtue ethics.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsubsection{The Formula of Universal Law \label{whyful}%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
Kant presents three formulations, or versions, 
of what he calls the ``supreme law of morality,'' but I focus on the first of these three. In this section, 
I argue that the Formula of Universal Law, specifically, is the easiest part of Kantian ethics to automate
and the most generalizable.

@@

Those who do not believe that all three formulations of the categorical imperative are equivalent
understand the FUL as the strongest or most foundational, and thus an appropriate initial choice for 
automation. Korsgaard characterizes the three formulations of the categorical
imperative according to Rawls' general and special conception of justice \cite{theoryofjustice}. The general conception 
consists of universal rules that can never be violated, no matter what the circumstances are. The special
conception, on the other hand, is an ideal to live up to, and in some cases, it may not be possible to 
achieve. For example, under some ethical theory, the general conception may include a prohibition against 
torturing others, whereas the the special conception may include the obligation to give to charity. 
In some situations, such as when a thief steals all your belongings and leaves you destitute, you may not 
be able to give to charity, but you are never allowed to torture others, no matter what the circumstances.
Korsgaard argues that the Formula of Universal Law represents Kant's general conception of justice, and the Formula of 
Humanity represents his special conception \citep[19]{KorsgaardRTL}. The FUL's prescriptions can never 
be violated, even in the most non-ideal circumstances imaginable, but the FUH is merely an ideal to 
strive towards. Thus, the FUL generates stronger requirements than the other two formulations and reflects 
the bare minimum standard of Kant's ethics. Because the FUL's prescriptions outweigh those of the other 
two formulations, it serves as a functional, minimal version of Kantian ethics.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsection{Dyadic Deontic Logic \label{ddl}%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
I formalize Kantian ethics by representing the Formula of Universal Law as an axiom on top of a base
logic. In this section, I present the logical background necessary to understand my work and my 
choice of Dyadic Deontic Logic (DDL).

@@

\isamarkupcmt{The blue text below is an example of typical Nitpick output. In this case, Nitpick successfully found a model 

@@

which is why this theorem was so easy to prove. I generated this proof automatically using Sledgehammer,
a tool that automatically searches for proofs \cite{sledgehammer}.%

@@

%:%102=52%:%
%:%114=54%:%

@@

%:%126=64%:%
%:%130=66%:%

@@

%:%158=93%:%
%:%162=95%:%

@@

%:%182=113%:%
%:%186=115%:%

@@

%:%206=134%:%
%:%210=137%:%

@@

%:%233=154%:%
%:%245=156%:%

@@

%:%265=174%:%
%:%269=176%:%

@@

%:%302=203%:%
%:%314=205%:%
%:%315=206%:%

@@

%:%373=263%:%
%:%377=265%:%
%:%378=266%:%
%:%379=267%:%

@@

%:%400=287%:%
%:%404=289%:%
%:%405=290%:%
%:%406=291%:%

@@

%:%439=317%:%
%:%451=319%:%
%:%452=320%:%
%:%453=321%:%
%:%454=322%:%

@@

%:%509=370%:%
%:%521=373%:%
%:%522=374%:%

@@

%:%591=437%:%
%:%603=439%:%
%:%604=440%:%

@@

%:%617=447%:%
%:%629=449%:%
%:%630=450%:%

@@

@@

%:%634=453%:%
%:%635=453%:%
%:%636=453%:%
%:%638=454%:%
%:%639=454%:%
%:%640=455%:%
%:%641=455%:%
%:%642=455%:%
%:%643=455%:%
%:%645=456%:%
%:%646=457%:%
%:%649=469%:%
%:%650=470%:%

@@

@@

%:%654=473%:%
%:%655=473%:%
%:%656=473%:%
%:%657=474%:%
%:%658=474%:%
%:%661=476%:%
%:%662=477%:%

@@

@@

%:%667=481%:%
%:%668=505%:%
%:%669=506%:%
%:%671=507%:%
%:%672=508%:%

@@

%:%682=515%:%
%:%694=517%:%
%:%695=518%:%

@@

%:%704=537%:%
%:%706=538%:%
%:%707=538%:%
%:%708=539%:%
%:%710=540%:%
%:%711=541%:%
%:%712=541%:%
%:%713=542%:%
%:%714=542%:%
%:%715=543%:%
%:%717=544%:%
%:%720=545%:%
%:%722=546%:%
%:%723=546%:%
%:%724=547%:%
%:%726=548%:%
%:%729=565%:%
%:%730=566%:%
%:%732=567%:%
%:%733=567%:%
%:%734=568%:%

@@

%:%736=569%:%
%:%737=570%:%

@@

%:%739=571%:%
%:%740=572%:%
%:%742=573%:%
%:%743=574%:%
%:%746=575%:%
%:%748=576%:%
%:%749=576%:%
%:%750=577%:%
%:%752=578%:%
%:%755=583%:%
%:%756=584%:%

@@

%:%761=590%:%
%:%762=590%:%
%:%763=590%:%
%:%765=590%:%
%:%769=590%:%
%:%770=590%:%
%:%772=591%:%
%:%773=592%:%
%:%774=592%:%
%:%776=593%:%
%:%777=594%:%

@@

%:%788=597%:%
%:%789=598%:%

@@
